\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-06 paper.tex
Fixed the URL issues in References

\includegraphics[width=1\textwidth,height=0.3\textheight]{paper_files/figure-pdf/fig-hex-param-1.pdf}

@@

\includegraphics[width=1\textwidth,height=0.3\textheight]{paper_files/figure-pdf/fig-p-d-error-in-2d-two-curvy-1.pdf}

@@

\caption{\label{fig-bins-two-curvy}Hexbin density plots of tSNE layout
of the two C-shaped clusters data, using three different bin inputs: (a)
\(b = 80 \text{ } (10, \text{ }8)\), (b)
\(b = 130 \text{ } (13, \text{ }10)\), and (c)
\(b = 391 \text{ } (23, \text{ }17)\). Color indicates standardized
counts, dark indicating high count and light indicates low count. At the
smallest bin size, the data structure is discontinuous, suggesting that
there are too many bins. Using the MSE of the model fit in
\(7\text{-}D\) helps decide on a useful choice of number of bins.}

@@

\includegraphics[width=1\textwidth,height=0.6\textheight]{paper_files/figure-pdf/fig-two_non_linear_diff_shaped_close_clusters-mse-1.pdf}

@@

{\centering \includegraphics[width=1\textwidth,height=0.9\textheight]{paper_files/figure-pdf/best-fit-umap-tsne-pacamp-1.pdf}

@@

\includegraphics[width=1\textwidth,height=1\textheight]{paper_files/figure-pdf/fig-pbmc-mse-1.pdf}

@@

\includegraphics[width=1\textwidth,height=0.8\textheight]{paper_files/figure-pdf/fig-model-pbmc-author-proj-1.pdf}

@@

\includegraphics[width=1\textwidth,height=1\textheight]{paper_files/figure-pdf/fig-pbmc-mse-umap-1.pdf}

@@

\includegraphics[width=1\textwidth,height=0.8\textheight]{paper_files/figure-pdf/fig-model-pbmc-author-proj-scdeed-1.pdf}

@@

\includegraphics[width=1\textwidth,height=1\textheight]{paper_files/figure-pdf/fig-mnist-mse-1.pdf}

@@

\includegraphics[width=1\textwidth,height=0.8\textheight]{paper_files/figure-pdf/fig-model-error-mnist-1.pdf}

>>>>

\includegraphics[width=0.3\textwidth,height=\textheight]{paper_files/figure-pdf/fig-hex-param-1.pdf}

@@

\includegraphics[width=0.3\textwidth,height=\textheight]{paper_files/figure-pdf/fig-p-d-error-in-2d-two-curvy-1.pdf}

@@

\caption{\label{fig-bins-two-curvy}Hexbin density plots of tSNE layout
of the two C-shaped clusters data, using three different bin inputs: (a)
\(b = 80 \text{ } (10, \text{ }8)\), (b)
\(b = 130 \text{ } (13, \text{ }10)\), and (c)
\(b = 391 \text{ } (23, \text{ }17)\). Color indicates standardized
counts, dark indicating high count and light indicates low count. At the
smallest bin size, the data structure is discontinuous, suggesting that
there are too many bins. Using the MSE of the model fit in
\(7\text{-}D\) helps decide on a useful choice of number of bins. XXX
All look the same}

@@

\includegraphics[width=0.6\textwidth,height=\textheight]{paper_files/figure-pdf/fig-two_non_linear_diff_shaped_close_clusters-mse-1.pdf}

@@

{\centering \includegraphics[width=0.9\textwidth,height=\textheight]{paper_files/figure-pdf/best-fit-umap-tsne-pacamp-1.pdf}

@@

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-pbmc-mse-1.pdf}

@@

\includegraphics[width=0.8\textwidth,height=\textheight]{paper_files/figure-pdf/fig-model-pbmc-author-proj-1.pdf}

@@

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-pbmc-mse-umap-1.pdf}

@@

\includegraphics[width=0.8\textwidth,height=\textheight]{paper_files/figure-pdf/fig-model-pbmc-author-proj-scdeed-1.pdf}

@@

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-mnist-mse-1.pdf}

@@

\includegraphics[width=0.8\textwidth,height=\textheight]{paper_files/figure-pdf/fig-model-error-mnist-1.pdf}
